HUME: Human UCCA-Based Evaluation of Machine Translation

### 2016-06-03 paper/main.tex
minor
moved footnote 7

Figure~\ref{fig:dacorrelation} plots the HUME score for each sentence against its DA score. HUME and Direct Assesment scores correlate reasonably well. The Pearson correlation for en-ro (en-de) is 0.70 (0.58), and 0.78 (0.74) where only doubly HUME-annotated points are taken. This confirms that HUME is consistent with an accepted human evaluation method, despite the differences in
their conception.
While DA is a valuable tool for MT research, HUME has two advantages:
it returns fine-grained semantic information about 
the quality of translations and it only requires very few annotators.
Direct assesment returns a single opaque score, and (as also noted by
Graham et al.), requires a large crowd which may not be available or reliable.

@@

We conducted an analysis of the English UCCA Wikipedia corpus (5324 sentences) in order to assess the pervasiveness of three phenomena that are not well supported by HMEANT.
First, copula clauses are treated in HMEANT simply as instances of the main verb ``be'', which generally does not convey the meaning of these clauses. They appear in 21.7\% of the sentences, according to conservative estimates that only consider non-auxiliary
instances of ``be''.
Second, nominal argument structures, ignored by HMEANT, are in fact highly
pervasive, appearing in 48.7\% of the sentences.
Third, linkers that express inter-relations between
clauses (mainly discourse markers and conjunctions) appear in 56\% of the
sentences, but are again ignored by HMEANT. As noted in our experiments, linkers
are sometimes omitted in translation, but these omissions are not taken
into consideration by HMEANT\footnote{Argument structures and linkers are explicitly marked in UCCA. Non-auxiliary instances of ``be'' and nouns are identified using the NLTK standard tagger. Nominal argument structures are here Scenes whose main relation is headed by a noun.}.

@@

\com{
\paragraph{Error Localisation.}
In HMEANT, an error in a child node often results in the parent node
being penalised as well. This makes it harder to quantify the true scale of  
the original error, as its effect gets propagated up the tree. 
In HUME, errors are localised as much as possible to where they occur,
by the separation of atomic and structural units,
which supports a more accurate aggregation of the translation errors
to a composite score.
}
\oa{Omitted point here}

>>>>

Figure~\ref{fig:dacorrelation} plots the HUME score for each sentence against
its DA score. HUME and Direct Assesment scores correlate reasonably well. The
Pearson correlation for en-ro (en-de) is 0.70 (0.58), and 0.78 (0.74) if only
doubly HUME-annotated points are considered. This confirms that HUME is consistent with an accepted human evaluation method, despite the differences in
their conception.
While DA is a valuable tool for MT research, HUME has two advantages:
it returns fine-grained semantic information about 
the quality of translations and it only requires very few annotators.
Direct assesment returns a single opaque score, and (as also noted by
Graham et al.), requires a large crowd which may not be available or reliable.

@@

We conducted an analysis of the English UCCA Wikipedia corpus (5324 sentences) in order to assess the pervasiveness of three phenomena that are not well supported by HMEANT.\footnote{Argument structures and linkers are explicitly marked in UCCA. Non-auxiliary instances of ``be'' and nouns are identified using the NLTK standard tagger. Nominal argument structures are here Scenes whose main relation is headed by a noun.}
First, copula clauses are treated in HMEANT simply as instances of the main verb ``be'', which generally does not convey the meaning of these clauses. They appear in 21.7\% of the sentences, according to conservative estimates that only consider non-auxiliary
instances of ``be''.
Second, nominal argument structures, ignored by HMEANT, are in fact highly
pervasive, appearing in 48.7\% of the sentences.
Third, linkers that express inter-relations between
clauses (mainly discourse markers and conjunctions) appear in 56\% of the
sentences, but are again ignored by HMEANT. As noted in our experiments, linkers
are sometimes omitted in translation, but these omissions are not taken
into consideration by HMEANT.

@@

\com{
\paragraph{Error Localisation.}
In HMEANT, an error in a child node often results in the parent node
being penalised as well. This makes it harder to quantify the true scale of  
the original error, as its effect gets propagated up the tree. 
In HUME, errors are localised as much as possible to where they occur,
by the separation of atomic and structural units,
which supports a more accurate aggregation of the translation errors
to a composite score.
}
%\oa{Omitted point here}
